---
title: "p8105_hw1_pl2848"
author: "Pei Liu"
date: "2022-09-23"
output: html_document
---

# Problem 1
Install a package containing the penguins dataset

load the penguins dataset
```{r}
data("penguins", package = "palmerpenguins")
```

Get basic info of penguins data set:
```{r}
summary(penguins)
```

Calculate the mean of flipper length, rows and columns of penguins data set
```{r}
mean(penguins$flipper_length_mm, na.rm = TRUE)
nrow(penguins)
ncol(penguins)
```

## Short Description of the penguins data set:
About this data set:

 1. Variables include species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex and year. The statistics are shown in the above chunk.
 
 2. There are 8 variables and 344 observations in this dataset.
 
 3. mean (flipper leangth) = 200.9152
 

# Problem 2
Load the tidyverse library
```{r}
library(tidyverse)
```

Create a dataframe as instructed:
```{r}
my_df = tibble(
  x = rnorm(10),
  y = x>0,
  z = "mailmansch",
  h = factor(c("1","3","2","3","3","2","1","1","1","2"), levels = c("1", "2", "3"), labels = c("red", "blue", "green"))
)
```

Try to calculate means of each variables in my_df:
```{r}
mean(my_df$x)
mean(my_df$y)
mean(my_df$z)
mean(my_df$h)
```

or use pull() to calculate:
```{r}
for (i in 1:4) {
mean <- my_df %>% 
  pull(i) %>% 
  mean()
print(mean)
}

```

**The above calculation shows that the means of numerical and logical can be calculated, while the means of character vector and factor vector can not be calculated.**

Convert variables y, z, h from their original types to numeric type:
```{r, echo = FALSE}
as.numeric(my_df$y)
as.numeric(my_df$z)
as.numeric(my_df$h)
```
as.numeric() function convert other types of variables to numerical variables. Because, in logical variable y, 0 represent False and 1 represent TRUE. In factor vector h, each level is represented by numbers.

This helps me to explain what happens when try to take the mean. We can only calculate means on numbers. Logical variables can convert to number 1 and 0; and factor vector can convert to number only when the level is number.

*Noted that, for character vectors, we can only convert them to numeric variable when numbers are in the "". *


