---
title: "p8105_hw1_pl2848"
author: "Pei Liu"
date: "2022-09-23"
output: html_document
---

# Problem 1
Install a package containing the penguins dataset

load the penguins dataset
```{r}
data("penguins", package = "palmerpenguins")
```

Get basic info of penguins data set:
```{r}
summary(penguins)
```

Calculate the mean of flipper length, rows and columns of penguins data set
```{r}
mean(penguins$flipper_length_mm, na.rm = TRUE)
nrow(penguins)
ncol(penguins)
```

## Short Description of the penguins data set:
About this data set:

 1. Variables include species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex and year. The statistics are shown in the above chunk.
 
 2. There are 8 variables and 344 observations in this dataset.
 
 3. mean (flipper leangth) = 200.9152
 

# Problem 2
Load the tidyverse library
```{r}
library(tidyverse)
```

Create a dataframe as instructed:
```{r}
my_df = tibble(
  x = rnorm(10),
  y = x>0,
  z = "mailmansch",
  h = c("red","blue","yellow","red","blue","blue","yellow","blue","red","blue")
)
```

